Scaling up the hyperparameter grid for Naomi

### 2023-07-13 src/dev_scale-grid/scale-grid.Rmd
Rename "pca_rescale" as "create_pca_grid" #58

gg3 <- pca_rescale(m = m, C = C, s = 3, k = 3)
nrow(mvQuad::getNodes(gg3))

gg5 <- pca_rescale(m = m, C = C, s = 5, k = 3)
nrow(mvQuad::getNodes(gg5))

gg7 <- pca_rescale(m = m, C = C, s = 7, k = 3)
nrow(mvQuad::getNodes(gg7))

gg9 <- pca_rescale(m = m, C = C, s = 9, k = 3)
nrow(mvQuad::getNodes(gg9))
```

@@

pca_grid_5 <- pca_rescale(m = m, C = C, s = 1, k = 5)

>>>>

gg3 <- create_pca_grid(m = m, C = C, s = 3, k = 3)
nrow(mvQuad::getNodes(gg3))

gg5 <- create_pca_grid(m = m, C = C, s = 5, k = 3)
nrow(mvQuad::getNodes(gg5))

gg7 <- create_pca_grid(m = m, C = C, s = 7, k = 3)
nrow(mvQuad::getNodes(gg7))

gg9 <- create_pca_grid(m = m, C = C, s = 9, k = 3)
nrow(mvQuad::getNodes(gg9))
```

@@

pca_grid_5 <- create_pca_grid(m = m, C = C, s = 1, k = 5)
